\begin{abstract}
Multi-agent systems can be extremely efficient when solving a team-wide task in a concurrent manner.
However, without proper synchronization, the correctness of the combined behavior is hard to guarantee,
such as to follow a specific ordering of sub-tasks or to perform a simultaneous collaboration.
This work addresses the minimum-time task planning problem for multi-agent systems
under complex global tasks stated as Linear Temporal Logic (LTL) formulas.
These tasks include the temporal and spatial requirements on both independent local actions and direct sub-team collaborations.
The proposed solution is an anytime algorithm that combines the partial-ordering analysis
of the underlying task automaton for task decomposition,
and the branch and bound (BnB) search method for task assignment.
Analyses of its soundness, completeness and optimality as the minimal completion time are provided.
It is also shown that a feasible and near-optimal solution is quickly reached while the search continues within the time budget.
Furthermore, to handle fluctuations in task duration and agent failures during online execution,
an adaptation algorithm is proposed to synchronize execution status and re-assign unfinished subtasks dynamically to maintain correctness and optimality.
Both algorithms are validated rigorously over large-scale systems via numerical simulations and hardware experiments,
against several strong baselines.
\end{abstract}


%==============
\begin{IEEEkeywords}
Networked Robots, Linear Temporal Logic, Task Coordination, Anytime Search.
\end{IEEEkeywords}
%=============================
