\begin{abstract}
Multi-agent systems can be efficient when solving a team-wide task in a concurrent manner.
However, without proper synchronization, the correctness of the combined behavior is hard to guarantee,
such as to follow a specific ordering of subtasks or to perform a simultaneous collaboration.
This work addresses the minimum-time task planning problem for multi-agent systems
under complex global tasks stated as syntactically co-safe Linear Temporal Logic (sc-LTL) formulas.
%这里改成scLTL
These tasks include the temporal and spatial requirements on both independent local actions and direct sub-team collaborations.
The proposed solution is an anytime algorithm that combines the partial-ordering analysis
of the underlying task automaton for task decomposition,
and the branch and bound (BnB) search method for task assignment.
\textcolor{blue}{We analyze the soundness, completeness and optimality regarding the minimal completion time.}
%Analyses of its soundness, completeness and optimality as the minimal completion time are provided.
\textcolor{blue}{We show that} a feasible and near-optimal solution is quickly reached while the search continues within the time budget.
Furthermore, to handle fluctuations in task duration and agent failures during online execution,
\textcolor{blue}{we propose} an adaptation algorithm to synchronize execution status and re-assign unfinished subtasks dynamically to maintain correctness and optimality.
\textcolor{blue}{Both algorithms are validated over systems of more than $10$ agents via numerical
simulations and hardware experiments, against several established baselines.}
\end{abstract}


%==============
\begin{keyword}
Networked Robots, Linear Temporal Logic, Task Coordination, Anytime Search.
\end{keyword}
%=============================
